---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  warning = FALSE,
  message = FALSE
)
```

# abstractsHostParasites

<!-- badges: start -->
<!-- badges: end -->

The goal of this R package abstractsHostParasites is to hold tools for generate
text classification models and process data associated with this task.


## Installation

You can install the development version of abstractsHostParasites from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("alrobles/abstractsHostParasites")
```
## Application case
The main goals of this project is to have a model that given an abstract
can classify if this abstrac belongs to a specific category.

An application case is to consider articles related to host-parasite interactions from open databases. In we case we get refered citations
in [Zover](http://www.mgc.ac.cn/cgi-bin/ZOVER/main.cgi) and Glogal mammal parasite database [GMPD](https://gmpd2.ecology.uga.edu/)




## Example

For this example we prepare two datasets, one with abstracts from ZOVER database
with host parasite interactions and other with random articles.

```{r example}
library(abstractsHostParasites)
library(tidyverse)

df_abstracts_zover <- readr::read_csv("https://raw.githubusercontent.com/alrobles/abstractsHostParasites/main/data-raw/zover_doi_abstract_date.csv")

df_abstracts_random <- readr::read_csv("https://raw.githubusercontent.com/alrobles/abstractsHostParasites/main/data-raw/df_abstracts_random.csv")
```

We join together this data sets and prepare for modelling. We add a class in each 
case. We set parasite class for zover abstracts and unknown class for random
abstracts. With do this with the help of `dplyr` functions

```{r example2}

df_abstracts_zover <- df_abstracts_zover %>% 
  select(doi, title, abstract) %>% 
  mutate(class = "parasite")

df_abstracts_random <- df_abstracts_random %>%
  sample_n(1000) %>% 
  select(doi, title, abstract) %>% 
  mutate(class = "unknown")

df_abstracts <- bind_rows(df_abstracts_zover, df_abstracts_random) %>%  
  sample_frac(1) %>% 
  na.exclude()
```


We finally use the `automodel_pu_abstracts` to classify this abstracts.
```{r example3}
models <- df_abstracts %>% 
  automodel_pu_abstracts(term_count = 1,
                         split_prop = 0.85,
                         doc_prop_max = 0.9,
                         doc_prop_min = 0)
```


We plot the final model just to look how it is.

```{r cars}
plot(models$model$fit.pi)
```



## Get in touch

By far, this approach can be used in different solutions.
If you are interested in any collaboration get in contact with [us](mailto:a.l.robles.fernandez@gmail.com)
