---
title: "Create a random abstracts dataset"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{randmAbstracts}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# Random abstracts
In this vignette we are going to build a random dataset of abstracts retriving information from [crossref](https://api.crossref.org/) api 

## First steps
First we install required packages 
```{r setup}
if(require(abstractsHostParasites)){
  devtools::install_github("alrobles/abstractsHostParasites")
}

if(require(tidyverse)){
  install.packages("tidyverse")
}

if(require(textcat)){
  install.packages("textcat")
}


```


First we create random table to show how it works the `rand_abstract_table` function. Ensure to provide a valid email address.

```{r}
abstractsHostParasites::rand_abstract_table("alroble8@asu.edu")
```

We replicate this function fifty times with `purrr::rerun` in order to have a list of 5000 random papers. This is because the crossref app only returns 100 records as maximum value. 

```{r}
# n = 50
n <-  2 #test with n = 2 because takes long time. 
List_random_abstracts <- n %>%
  purrr::rerun(abstractsHostParasites::rand_abstract_table("alroble8@asu.edu"))

```

We reduce this list to a single `data.frame` using `purrr::reduce` and `dplyr::bind_rows` functions from `dplyr` package.

```{r echo=FALSE}
df_abstracts_random <- List_random_abstracts %>% purrr::reduce(dplyr::bind_rows)
```

Follow this we clean our abstractas using `prep_fun`. This functions convert the string of the abstract to lower case and eliminate repeated spaces and line breaks. We also trim whitespace (with `stringr::str_trim` function) from the abstract and only keep the files selection doi, title and abstract.

```{r echo = FALSE}
df_abstracts_random <- df_abstracts_random %>%
  dplyr::mutate(abstract = abstractsHostParasites::prep_fun(abstract) ) %>%
  dplyr::mutate(abstract = stringr::str_trim(abstract)) %>%
  dplyr::select(doi, title, abstract)
```

We are going to filter now only the english abstracts. We use the `textcat`function to identify the language and storage in a new variable with the help of `dplyr::mutate` function. Follow this we filter only abstracts in english language.

```{r echo = FALSE}
df_abstracts_random <- df_abstracts_random %>%
  dplyr::mutate(language = textcat::textcat(abstract)) %>%
  dplyr::filter(language == "english")
```

Finally we create a new variable called class whe we label this papers as unknown ready to be modeled in our PU learning (Positive and unlabeled) framework.

```{r echo = FALSE}
df_abstracts_random <- df_abstracts_random %>% dplyr::mutate(class = "unknown")

```


